Tidy data structure to support exploration and modeling of temporal data

### 2018-12-25 main.Rmd
added animated window plots

\begin{table}[!hbt]
\caption{A list of table verbs working with tsibble. Functions in bold originating from the tidyverse and are adapted for tsibble.}\label{tab:verb-table}
\centering
\begin{tabular}{ lll }
\toprule
 & Verb & Description \\ \midrule
\multirow{4}{*}{Time gaps} & \texttt{has\_gaps()} & Test if a tsibble has gaps in time \\
 & \texttt{scan\_gaps()} & Report implicit missing entries \\
 & \texttt{count\_gaps()} & Summarize time gaps \\
 & \texttt{fill\_gaps()} & Fill in gaps by values and functions \\ \hline
\multirow{4}{*}{Row-wise} & \textbf{\texttt{filter()}} & Pick rows based on conditions \\
 & \texttt{filter\_index()} & Provide a shorthand for time subsetting \\
 & \textbf{\texttt{slice()}} & Select rows based on row positions \\
 & \textbf{\texttt{arrange()}} & Sort the ordering of row by variables \\ \hline
\multirow{4}{*}{Column-wise} & \textbf{\texttt{select()}} & Pick columns by variables \\
 & \textbf{\texttt{mutate()}} & Add new variables \\
 & \textbf{\texttt{transmute()}} & Drops existing variables \\
 & \textbf{\texttt{summarise()}} & Aggregate values over time \\ \hline
\multirow{3}{*}{Group-wise} & \texttt{index\_by()} & Group by new time index \\
 & \textbf{\texttt{group\_by()}} & Group by one or more variables \\
 & \texttt{group\_by\_key()} & Group by key variables \\ \hline
\multirow{4}{*}{Reshape} & \textbf{\texttt{gather()}} & Gather columns into long form \\
 & \textbf{\texttt{spread()}} & Spread columns into wide form \\
 & \textbf{\texttt{nest()}} & Nest values in a list-variable \\
 & \textbf{\texttt{unnest()}} & Unnest a list-variable \\ \hline
\multirow{6}{*}{Join tables} & \textbf{\texttt{left\_join()}} & \multirow{6}{*}{Join two tables together} \\
 & \textbf{\texttt{right\_join()}} & \\
 & \textbf{\texttt{full\_join()}} & \\
 & \textbf{\texttt{inner\_join()}} & \\
 & \textbf{\texttt{semi\_join()}} & \\
 & \textbf{\texttt{anti\_join()}} & \\
\bottomrule
\end{tabular}
\end{table}

@@

>>>>

\begin{table}[!hbt]
\caption{A list of table verbs working with tsibble. Functions in bold originating from the tidyverse and are adapted for tsibble.}\label{tab:verb-table}
\centering
\begin{tabular}{ lll }
\toprule
 & Verb & Description \\ \midrule
\multirow{4}{*}{Time gaps} & \texttt{has\_gaps()} & Test if a tsibble has gaps in time \\
 & \texttt{scan\_gaps()} & Report implicit missing entries \\
 & \texttt{count\_gaps()} & Summarize time gaps \\
 & \texttt{fill\_gaps()} & Fill in gaps by values and functions \\ \hline
\multirow{4}{*}{Row-wise} & \textbf{\texttt{filter()}} & Pick rows based on conditions \\
 & \texttt{filter\_index()} & Provide a shorthand for time subsetting \\
 & \textbf{\texttt{slice()}} & Select rows based on row positions \\
 & \textbf{\texttt{arrange()}} & Sort the ordering of row by variables \\ \hline
\multirow{4}{*}{Column-wise} & \textbf{\texttt{select()}} & Pick columns by variables \\
 & \textbf{\texttt{mutate()}} & Add new variables \\
 & \textbf{\texttt{transmute()}} & Drops existing variables \\
 & \textbf{\texttt{summarise()}} & Aggregate values over time \\ \hline
\multirow{3}{*}{Group-wise} & \texttt{index\_by()} & Group by index candidate \\
 & \textbf{\texttt{group\_by()}} & Group by one or more variables \\
 & \texttt{group\_by\_key()} & Group by key variables \\ \hline
\multirow{4}{*}{Reshape} & \textbf{\texttt{gather()}} & Gather columns into long form \\
 & \textbf{\texttt{spread()}} & Spread columns into wide form \\
 & \textbf{\texttt{nest()}} & Nest values in a list-variable \\
 & \textbf{\texttt{unnest()}} & Unnest a list-variable \\ \hline
\multirow{6}{*}{Join tables} & \textbf{\texttt{left\_join()}} & \multirow{6}{*}{Join two tables together} \\
 & \textbf{\texttt{right\_join()}} & \\
 & \textbf{\texttt{full\_join()}} & \\
 & \textbf{\texttt{inner\_join()}} & \\
 & \textbf{\texttt{semi\_join()}} & \\
 & \textbf{\texttt{anti\_join()}} & \\
\bottomrule
\end{tabular}
\end{table}

@@

```{r tb-au}
```

```{r slide-animate, fig.show = "animate", fig.height = 2.5, fig.cap = "(ref:slide-animate-cap)"}
```

(ref:slide-animate-cap) An illustration of window of size 5 sliding over annual tuberculosis cases in Australia. View the animation with Adobe Acrobat Reader.

```{r tile-animate, fig.show = "animate", fig.height = 2.5, fig.cap = "(ref:tile-aniamte-cap)"}
```

(ref:tile-animate-cap) An illustration of window of size 5 tiling over annual tuberculosis cases in Australia. View the animation with Adobe Acrobat Reader.

```{r stretch-animate, fig.show = "animate", fig.height = 2.5, fig.cap = "(ref:stretch-animate-cap)"}
```

(ref:stretch-animate-cap) An illustration of window of size 5 stretching over annual tuberculosis cases in Australia. View the animation with Adobe Acrobat Reader.
